|

### 2025-10-23 manuscript/pre_print.qmd
Update to quarto last modified date and long format

---
title: |
  Does resting energy expenditure differ between women with and without polycystic ovary syndrome (PCOS): a systematic review and meta-analysis
date: 'format(Sys.time(), "%b %d, %Y")'
format:
  pdf:
    include-in-header:
      text: |
       \usepackage[font=scriptsize]{caption}
       \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
author:
  - name: Richard Kirwan
    affiliations:
      - ref: 1
    orcid: 0000-0003-4645-0077
    corresponding: true
    email: R.P.Kirwan@ljmu.ac.uk
  - name: Leigh Peele
    affiliations:
      - ref: 2
    email: leigh@macrofactorapp.com
  - name: Greg Nuckols
    affiliations:
      - ref: 2
    orcid: 0009-0004-2679-7967
    email: greg@macrofactorapp.com
  - name: Georgia Kohlhoff
    affiliations:
      - ref: 3
    # orcid: 0000-0002-8003-0757
    email: g_kohlhoff@hotmail.co.uk
  - name: Hannah Cabré
    affiliations:
      - ref: 4
    orcid: 0000-0002-3235-6867
    email: Hannah.Cabre@pbrc.edu
  - name: Alyssa Olenick
    affiliations:
      - ref: 5
    orcid: 0000-0002-2217-8067
    corresponding: true
    email: alyssaolenickphd@gmail.com
  - name: James Steele
    affiliations:
      - ref: 6
      - ref: 2
      - ref: 7
    orcid: 0000-0002-8003-0757
    corresponding: true
    email: james@steele-research.com
affiliations:
  - id: 1
    name: Research Institute for Sports and Exercise Sciences, Liverpool John Moores Universtiy, Liverpool, UK
  - id: 2
    name: MacroFactor, Stronger by Science LLC, Raleigh, North Carolina, USA
  - id: 3
    name: Flourishing Health, Liverpool, UK
  - id: 4
    name: Reproductive Endocrinology and Women’s Health Research Program, Pennington Biomedical Research Center, Baton Rouge, Louisiana, USA
  - id: 5
    name: Dr Alyssa Olenick LLC
  - id: 6
    name: Steele Research Limited, Eastleigh, Hampshire, UK
  - id: 7
    name: School of Health and Biomedical Sciences, Royal Melbourne Institute of Technology, Melbourne, VIC, Australia
abstract: |
  Background: Polycystic ovary syndrome is the most common endocrine condition affecting women of reproductive age. Overweight and obesity in women with PCOS is commonly deemed a result of a lower basal metabolic rate (BMR), which has influenced lifestyle-based interventions in this group. Evidence supporting this reduced, however, is not consistent. Objectives: To systematically search and meta-analyse the existing literature to determine if resting energy expenditure differs between women with and without polycystic ovary syndrome (PCOS). Design: A systematic search was conducted using PubMed, Medline and Web of Science databases from January 1990 to January 2025. Studies that assessed resting energy expenditure in women with and without PCOS were included. Results: 18 studies were identified. Study populations ranged from X to X participants, with mean ages ranging from X to X years. Conclusions: TO ADD
keywords: Polycystic ovary syndrome, PCOS, resting energy expenditure, REE, basal metabolic rate, BMR
bibliography: 
  mylibrary.bib
csl: apa.csl
execute: 
  echo: false
  message: false
  warning: false
---
```{r}
library(tidyverse)
library(flextable)
library(tidybayes)

>>>>

---
title: |
  Does resting energy expenditure differ between women with and without polycystic ovary syndrome (PCOS): a systematic review and meta-analysis
date: last-modified
date-format: long
format:
  pdf:
    include-in-header:
      text: |
       \usepackage[font=scriptsize]{caption}
       \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
author:
  - name: Richard Kirwan
    affiliations:
      - ref: 1
    orcid: 0000-0003-4645-0077
    corresponding: true
    email: R.P.Kirwan@ljmu.ac.uk
  - name: Leigh Peele
    affiliations:
      - ref: 2
    email: leigh@macrofactorapp.com
  - name: Greg Nuckols
    affiliations:
      - ref: 2
    orcid: 0009-0004-2679-7967
    email: greg@macrofactorapp.com
  - name: Georgia Kohlhoff
    affiliations:
      - ref: 3
    # orcid: 0000-0002-8003-0757
    email: g_kohlhoff@hotmail.co.uk
  - name: Hannah Cabré
    affiliations:
      - ref: 4
    orcid: 0000-0002-3235-6867
    email: Hannah.Cabre@pbrc.edu
  - name: Alyssa Olenick
    affiliations:
      - ref: 5
    orcid: 0000-0002-2217-8067
    corresponding: true
    email: alyssaolenickphd@gmail.com
  - name: James Steele
    affiliations:
      - ref: 6
      - ref: 2
      - ref: 7
    orcid: 0000-0002-8003-0757
    corresponding: true
    email: james@steele-research.com
affiliations:
  - id: 1
    name: Research Institute for Sports and Exercise Sciences, Liverpool John Moores Universtiy, Liverpool, UK
  - id: 2
    name: MacroFactor, Stronger by Science LLC, Raleigh, North Carolina, USA
  - id: 3
    name: Flourishing Health, Liverpool, UK
  - id: 4
    name: Reproductive Endocrinology and Women’s Health Research Program, Pennington Biomedical Research Center, Baton Rouge, Louisiana, USA
  - id: 5
    name: Dr Alyssa Olenick LLC
  - id: 6
    name: Steele Research Limited, Eastleigh, Hampshire, UK
  - id: 7
    name: School of Health and Biomedical Sciences, Royal Melbourne Institute of Technology, Melbourne, VIC, Australia
abstract: |
  Background: Polycystic ovary syndrome is the most common endocrine condition affecting women of reproductive age. Overweight and obesity in women with PCOS is commonly deemed a result of a lower basal metabolic rate (BMR), which has influenced lifestyle-based interventions in this group. Evidence supporting this reduced, however, is not consistent. Objectives: To systematically search and meta-analyse the existing literature to determine if resting energy expenditure differs between women with and without polycystic ovary syndrome (PCOS). Design: A systematic search was conducted using PubMed, Medline and Web of Science databases from January 1990 to January 2025. Studies that assessed resting energy expenditure in women with and without PCOS were included. Results: 18 studies were identified. Study populations ranged from X to X participants, with mean ages ranging from X to X years. Conclusions: TO ADD
keywords: Polycystic ovary syndrome, PCOS, resting energy expenditure, REE, basal metabolic rate, BMR
bibliography: 
  mylibrary.bib
csl: apa.csl
execute: 
  echo: false
  message: false
  warning: false
---
```{r}
library(tidyverse)
library(flextable)
library(tidybayes)
